GEE models

### 2017-07-05 doc/manuscript.Rmd
updated wording and covariates of gee model in methods

Covariate selection was based on previous literature, directed acyclic graph 
[@Greenland1999a] recommendations, and quasi-likelihood information criterion 
(QIC). `r cite_st('qic')` shows the covariates compared using QIC. While the
final GEE model selected as best fitting differed between insulin sensitivity
and beta-cell function measures, the differences in QIC values were less than
10 between the models, suggesting similar fit. As such, we selected the model
that had the fewest covariates and that had similar fit between the outcome
measures (M8). The final GEE model was adjusted for time, sex, ethnicity,
baseline age, WC, ALT, and family history of diabetes. Sex, ethnicity, and baseline 
age were time-*independent* variables. After scaling,
log-transforming, and exponentiating, the GEE estimates are
interpreted as an expected percent difference in the outcome variable for every
standard deviation (SD) increase in the predictor variable given the covariates are held constant.
Since TAG is a risk factor for diabetes and since NEFA contribute to TAG
production, TAG may act as a mediator between NEFA and the outcomes. To
determine the role of TAG in the association between NEFA and the outcomes, TAG
was included in the GEE model as a sensitivity analysis. Lastly for the GEE
models, we tested for an interaction with sex, ethnicity, or time by the
predictor term for each outcome variable.

>>>>

Covariate selection was based on previous literature, directed acyclic graph 
[@Greenland1999a] recommendations (see `r cite_sf("dag")`), and quasi-likelihood information criterion 
(QIC). `r cite_st('qic')` shows the covariates compared using QIC. To reduce
complexity between models using either insulin sensitivity or beta-cell function
measures, only the model that had similar good fit for both was used. 
As such, we selected the model
that had the fewest covariates and that had similar fit between the outcome
measures (M9). The final GEE model was adjusted for years from baseline (time),
sex (female or male), ethnicity (European ancestry or non-European ancestry),
baseline age, WC, ALT, and MET (physical activity). Sex, ethnicity, and baseline 
age were time-*independent* variables. After scaling,
log-transforming, and exponentiating, the GEE estimates are
interpreted as an expected percent difference in the outcome variable for every
standard deviation (SD) increase in the predictor variable given the covariates
are held constant.
Since TAG is a risk factor for diabetes and since NEFA contribute to TAG
production, TAG may act as a mediator between NEFA and the outcomes. To
determine the role of TAG in the association between NEFA and the outcomes, TAG
was included in the GEE model as a sensitivity analysis. Lastly for the GEE
models, we tested for an interaction with sex, ethnicity, or time by the
predictor term for each outcome variable.
